---
title: "Flow_Cytometry_GAP1:GFP Screen Analysis"
author: "Nathan Brandt"
date: "Sept 19th, 2016"
output: html_document
---
#1) Two samples in four media types analyzed on the Accuri in triplicate .
#    Strains-
#     GAP1::GFP KO Collection Pool
#     Strains have GFP fused with GAP1 and tdTomato expressed under the ACT1 promoter in the HO locus
#    Media Types-
#     SC
#     Proline Limited Media
#   Controls-
#      FY4 in Proline Limited Media
#      FY4 in SC Media
#      GFP::GAP1 HISKO in Proline Limited Media
#      GFP::GAP1 HISKO in SC Media

###This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters
* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed

******
##Step 1: Load relevant libraries 

```{r}
#Load libraries
library(flowCore)
library(flowViz)
library(flowQ)
library(flowStats)
library(Hmisc)
library(reshape2)
library(ggplot2)
library(flowWorkspace)
library(ggcyto)
library(gridExtra)
```

###Step 2: Read in all .fcs files in current directory and a sample sheet that contains four columns with 
* column1 = Well
* column2 = Strain
* column3 = Genotype
* column4 = Ploidy
* column5 = Media


```{r}
#Set working directory to the folder in which you have stored your .fcs files
#Read in all the fcs files in the directory, with alter.ames changing "-" to "."

path.data <-"~/Google Drive/Transfer_Folder/" #location of data files
path.save <-"~/Flow_Cytometry_Analysis/CarryOverScreen/Reports/"#location to save files

 #Create Folders to store pdf files

samplesize <- NULL #Number of Random Lines from the FSC files to read in, set to NULL to read all lines

flowData <- read.flowSet(path = paste(path.data,"Well_Cross_Over_Test", sep=""), pattern=".fcs", which.lines=samplesize, alter.names=TRUE)

sample.sheet <- read.csv(paste(path.data,"Well_Cross_Over_Test/SampleSheet.csv", sep=""))

#Adds a Strain identifier to the pData
pData(flowData)$strain <- sample.sheet$Strain

```

#Gating of data, and filtering
```{r}

##Apply a rectangle gate based on FSC and SSC to remove values that we have determined are typically debris for haploid cells.  This should be adjusted if the cell type is different
rectGate <- rectangleGate("FSC.A"= c(5.6,7.6),"SSC.A" = c(4.6,6.8))

boundaries <- matrix(c(2e5,6e5,1.5e6,5e6,1.5e6,5e5,3e5,2.5e4,2.5e4,1e5,1e6,1e6,5e5,3e5),ncol=2,nrow=7)
colnames(boundaries) <- c("FSC.A","SSC.A")
polyGate <- sapply(sampleNames(flowData),function(sn)polygonGate(.gate = boundaries))

#Subset the filtered data to remove outliers defined by FFC and SSC 
filterData <- flowData#Subset(flowData, rectGate) 
```



#Transfer data into a dataframe and produce summary stats
```{r}
#Summary Statistics of Normalized Filtered Data
#Move filtered data into a dataframe
filter.data <- data.frame(FSC.A=NA,SSC.A=NA,FL1.A=NA,WELL=NA,STRAIN=NA)
stats.data <- data.frame(WELL=NA,STRAIN=NA,COUNT=NA,MEDIAN=NA,MEAN=NA,SD=NA,VAR=NA)

for(i in 1:length(filterData)){
  fsc.a <- exprs(filterData[[i,1]])
  ssc.a <- exprs(filterData[[i,2]])
  fl1.a <- exprs(filterData[[i,3]])
  well <- unlist(strsplit(rownames(pData(filterData)),'.fcs'))[i]
  strain <- as.character(sample.sheet[i,2])
  
  filter.data<-rbind(filter.data,cbind(FSC.A=fsc.a,SSC.A=ssc.a,FL1.A=fl1.a,WELL=well,STRAIN=strain))
  
  stats.data<-(rbind(stats.data,cbind(WELL=well,STRAIN=strain,COUNT=length(fsc.a),MEDIAN=median(fl1.a/fsc.a),MEAN=mean(fl1.a/fsc.a),SD=sd(fl1.a/fsc.a),VAR=as.numeric(var(fl1.a/fsc.a)))))
}  
  
 #Cleans up DataFrames
  filter.data<-filter.data[2:nrow(filter.data),]
  filter.data$FSC.A<-as.numeric(filter.data$FSC.A)
  filter.data$SSC.A<-as.numeric(filter.data$SSC.A)
  filter.data$FL1.A<-as.numeric(filter.data$FL1.A)
  filter.data$WELL<-as.factor(filter.data$WELL)
  filter.data$STRAIN<-as.factor(filter.data$STRAIN)
  
  stats.data<-stats.data[2:nrow(stats.data),]
  stats.data$WELL<-as.factor(stats.data$WELL)
  stats.data$STRAIN<-as.factor(stats.data$STRAIN)
  stats.data$COUNT<-as.numeric(stats.data$COUNT)
  stats.data$MEDIAN<-as.numeric(stats.data$MEDIAN)
  stats.data$MEAN<-as.numeric(stats.data$MEAN)    
  stats.data$SD<-as.numeric(stats.data$SD)
  stats.data$VAR<-as.numeric(stats.data$VAR)
  
```


#Plots of Data
```{r eval=FALSE}
  # Set to FALSE because I want to only look at the flagged data
  #Plots all the wells forward vs side plots, and the boxplots of the various paramenters, and OD
#Plots of FSC VS SSC
ggplot(subset(filter.data, filter.data$WELL==sample.sheet$Well[1:12]), aes(x = FSC.A, y = SSC.A))+
    geom_hex(bins=512)+
    facet_wrap(~ WELL + STRAIN,ncol=6)+
    theme(legend.position="none")+
    scale_x_log10()+
    scale_y_log10()

#Plots of FSC VS FL1
ggplot(subset(filter.data, filter.data$WELL==sample.sheet$Well[1:12]), aes(x = FSC.A, y = FL1.A))+
    geom_hex(bins=128)+
    facet_wrap(~ WELL + STRAIN,ncol=6)+
    theme(legend.position="none")+
    scale_x_log10()+
    scale_y_log10()

ggplot(subset(filter.data, filter.data$WELL==sample.sheet$Well[13:24]), aes(x = FSC.A, y = FL1.A))+
    geom_hex(bins=128)+
    facet_wrap(~ WELL + STRAIN,ncol=6)+
    theme(legend.position="none")+
    scale_x_log10()+
    scale_y_log10()

ggplot(subset(filter.data, filter.data$WELL==sample.sheet$Well[25:36]), aes(x = FSC.A, y = FL1.A))+
    geom_hex(bins=128)+
    facet_wrap(~ WELL + STRAIN,ncol=6)+
    theme(legend.position="none")+
    scale_x_log10()+
    scale_y_log10()

ggplot(subset(filter.data, filter.data$WELL==sample.sheet$Well[37:48]), aes(x = FSC.A, y = FL1.A))+
    geom_hex(bins=128)+
    facet_wrap(~ WELL + STRAIN,ncol=6)+
    theme(legend.position="none")+
    scale_x_log10()+
    scale_y_log10()

#ggsave(paste(path.save,"Plate",plate,"_PDFs/FSC.AvsSSC.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), plot=size.plots height=8, width=12)
    
    
#Plots of FSC Data
ggplot(filter.data, aes(WELL,FSC.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= paste("FSC.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/FSC.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)

#Plots of SSC Data
ggplot(filter.data, aes(WELL,SSC.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= paste("SSC.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/SSC.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)

#Plot of FL1 Data
ggplot(filter.data, aes(WELL,FL1.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= paste("FL1.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/F1.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)

#Plot of FL1/FSC Data
ggplot(filter.data, aes(WELL,(FL1.A/FSC.A))) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= paste("FL1.A/FSC.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/FL1.ANormFSC.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)


```