---
title: "Flow_Cytometry_GAP1:GFP Screen Analysis"
author: "Nathan Brandt"
date: "Sept 19th, 2016"
output: html_document
---
#1) Two samples in four media types analyzed on the Accuri in triplicate .
#    Strains-
#     GAP1::GFP KO Collection Pool
#     Strains have GFP fused with GAP1 and tdTomato expressed under the ACT1 promoter in the HO locus
#    Media Types-
#     SC
#     Proline Limited Media
#   Controls-
#      FY4 in Proline Limited Media
#      FY4 in SC Media
#      GFP::GAP1 HISKO in Proline Limited Media
#      GFP::GAP1 HISKO in SC Media

###This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters
* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed

******
##Step 1: Load relevant libraries 

```{r}
#Load libraries
library(flowCore)
library(flowViz)
#library(flowQ) #Not Availible in R 3.3.1
library(flowStats)
library(Hmisc)
library(reshape2)
library(ggplot2)
library(flowWorkspace)
library(ggcyto)
```

###Step 2: Read in all .fcs files in current directory and a sample sheet that contains four columns with 
* column1 = Well
* column2 = Strain
* column3 = Genotype
* column4 = Ploidy
* column5 = Media

#Calculate Statistics Utilizing All sampled events
```{r}
#Set working directory to the folder in which you have stored your .fcs files
#Read in all the fcs files in the directory, with alter.ames changing "-" to "."

plate <- "01" #Plate under 10 need 0#
condition <- "ProLim" #SC or ProLim
path.data <-"~/Google Drive/Transfer_Folder/" #location of data files
dir.create("~/Flow_Cytometry_Analysis/GAP1_GFP_Screen_09192016/SamplingReports/")
path.save <-"~/Flow_Cytometry_Analysis/GAP1_GFP_Screen_09192016/SamplingReports/"#location to save files

samplesize <- NULL #Number of Random Lines from the FSC files to read in, set to NULL to read all lines

  flowData <- read.flowSet(path = paste(path.data,"GAP1_GFP_Screen_FSC_Files/Plate",plate,"_",condition, sep=""), pattern=".fcs", which.lines=samplesize, alter.names=TRUE)

  sample.sheet <- read.csv(paste(path.data,"GAP1_GFP_Screen_DataSheets/Plate",plate,"_",condition,".csv", sep=""))

filterData <- flowData

  #Summary Statistics of Normalized Filtered Data
  stats.data.all <- data.frame(WELL=NA,STRAIN=NA,SAMPLESIZE=NA,COUNT=NA,MEDIAN=NA,MEAN=NA,SD=NA,VAR=NA)

  for(i in 1:length(filterData)){
    fsc.a <- exprs(filterData[[i,1]])
    fl1.a <- exprs(filterData[[i,3]])
    well <- unlist(strsplit(rownames(pData(filterData)),'.fcs'))[i]
    strain <- as.character(sample.sheet[i,2])
  
    stats.data.all<-(rbind(stats.data.all,cbind(WELL=well,STRAIN=strain,SAMPLESIZE=10000,COUNT=length(fsc.a),MEDIAN=median(fl1.a/fsc.a),MEAN=mean(fl1.a/fsc.a),SD=sd(fl1.a/fsc.a),VAR=as.numeric(var(fl1.a/fsc.a)))))
    }  
  
 #Cleans up DataFrames
    stats.data.all<-stats.data.all[2:nrow(stats.data.all),]
    stats.data.all$WELL<-as.factor(stats.data.all$WELL)
    stats.data.all$STRAIN<-as.factor(stats.data.all$STRAIN)
    stats.data.all$SAMPLESIZE<-as.numeric(stats.data.all$SAMPLESIZE)
    stats.data.all$COUNT<-as.numeric(stats.data.all$COUNT)
    stats.data.all$MEDIAN<-as.numeric(stats.data.all$MEDIAN)
    stats.data.all$MEAN<-as.numeric(stats.data.all$MEAN)    
    stats.data.all$SD<-as.numeric(stats.data.all$SD)
    stats.data.all$VAR<-as.numeric(stats.data.all$VAR)
```

#Calculate Statistics Utilizing a subset of sampled events
```{r}

plate.condition.df <- data.frame(PLATE=c(rep('01',2),rep('02',2),rep('03',2),rep('04',2),rep('05',2)),CONDITION=rep(c('ProLim','SC'),5))  
     m2e.df <- data.frame(SAMPLESIZE=NA,M2E=NA,PLATE=NA,CONDITION=NA)

    
sample.size.list <- c(100,200,500,1000,2000,5000)
for(y in 1:100){
  print(y)
for(x in 1:2){
  stats.data <- data.frame(WELL=NA,STRAIN=NA,SAMPLESIZE=NA,COUNT=NA,MEDIAN=NA,MEAN=NA,SD=NA,VAR=NA)
     sample.sheet <- read.csv(paste(path.data,"GAP1_GFP_Screen_DataSheets/Plate",plate.condition.df$PLATE[x],"_",plate.condition.df$CONDITION[x],".csv", sep=""))  
  
  for(z in 1:6){
    samplesize <- sample.size.list[z] #Number of Random Lines from the FSC files to read in, set to NULL to read all lines

    flowData <- read.flowSet(path = paste(path.data,"GAP1_GFP_Screen_FSC_Files/Plate",plate.condition.df$PLATE[x],"_",plate.condition.df$CONDITION[x], sep=""), pattern=".fcs", which.lines=samplesize, alter.names=TRUE)


    filterData <- flowData

#Summary Statistics of Normalized Filtered Data
#Move filtered data into a dataframe
  

    for(i in 1:length(filterData)){
      fsc.a <- exprs(filterData[[i,1]])
      #ssc.a <- exprs(filterData[[i,2]])
      fl1.a <- exprs(filterData[[i,3]])
      well <- unlist(strsplit(rownames(pData(filterData)),'.fcs'))[i]
      strain <- as.character(sample.sheet[i,2])
  
      stats.data<-(rbind(stats.data,cbind(WELL=well,STRAIN=strain,SAMPLESIZE=sample.size.list[z],COUNT=length(fsc.a),MEDIAN=median(fl1.a/fsc.a),MEAN=mean(fl1.a/fsc.a),SD=sd(fl1.a/fsc.a),VAR=as.numeric(var(fl1.a/fsc.a)))))
    }  
  }

#Cleans up DataFrames
      stats.data<-stats.data[2:nrow(stats.data),]
      stats.data$WELL<-as.factor(stats.data$WELL)
      stats.data$STRAIN<-as.factor(stats.data$STRAIN)          
      stats.data.all$SAMPLESIZE<-as.numeric(stats.data.all$SAMPLESIZE)
      stats.data$COUNT<-as.numeric(stats.data$COUNT)
      stats.data$MEDIAN<-as.numeric(stats.data$MEDIAN)
      stats.data$MEAN<-as.numeric(stats.data$MEAN)    
      stats.data$SD<-as.numeric(stats.data$SD)
      stats.data$VAR<-as.numeric(stats.data$VAR)

#```

#Calculating Mean Squared Error
#```{r}
    
      for(z in 1:6){
       sum.m2e <-0
      for(i in 1:96){
          sum.m2e <- sum.m2e + (stats.data$MEAN[(stats.data$WELL==sample.sheet$Well[i])&(stats.data$SAMPLESIZE==sample.size.list[z])]
-stats.data.all$MEAN[stats.data.all$WELL==sample.sheet$Well[i]])^2
      }
      m2e <- sum.m2e/96
      m2e.df <- rbind(m2e.df, cbind(SAMPLESIZE=sample.size.list[z],M2E=m2e,PLATE=plate.condition.df$PLATE[x],CONDITION=as.character(plate.condition.df$CONDITION[x])))
      }
       sum.m2e <-0
       for(i in 1:96){
          sum.m2e <- sum.m2e + (stats.data.all$MEAN[stats.data.all$WELL==sample.sheet$Well[i]]
-stats.data.all$MEAN[stats.data.all$WELL==sample.sheet$Well[i]])^2
      }
      m2e <- sum.m2e/96
      m2e.df <- rbind(m2e.df, cbind(SAMPLESIZE=10000,M2E=m2e,PLATE=plate.condition.df$PLATE[x],CONDITION=as.character(plate.condition.df$CONDITION[x])))
    
}
}
      m2e.df<-m2e.df[2:nrow(m2e.df),]
             
      m2e.df$SAMPLESIZE<-as.factor(m2e.df$SAMPLESIZE)
      m2e.df$M2E<-as.numeric(m2e.df$M2E)
       m2e.df$PLATE<-as.factor(m2e.df$PLATE)
      m2e.df$CONDITION<-as.factor(m2e.df$CONDITION)  

```

#Note try to convert to think it in terms of precent error, take the square root of the value and take the actual measured quantiy. Take the average quanity over the 96 measurements and try to look at it as a fraction of the total mean of the plate.

```{r eval=FALSE}
#Plots of Data
  boxplot.stats(subset(m2e.df, m2e.df$CONDITION=='ProLim'))
ggplot(subset(m2e.df, m2e.df$CONDITION=='ProLim'), aes(SAMPLESIZE,M2E)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= "PLATE01_PROLIM_RANDOM_SAMPLE_X100")+
    xlab("SAMPLESIZE")
      
ggsave(paste(path.save,"PLATE01_PROLIM_RANDOM_SAMPLE_X100.pdf"), height=8, width=12)

ggplot(subset(m2e.df, (m2e.df$CONDITION=='SC' & m2e.df$SAMPLESIZE!=10000)), aes(SAMPLESIZE,M2E)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= "PLATE01_SC_RANDOM_SAMPLE_X100") +
    xlab("SAMPLESIZE")      
ggsave(paste(path.save,"PLATE01_SC_RANDOM_SAMPLE_X100.pdf",sep=""), height=8, width=12)

```