---
title: "Flow_Cytometry_GAP1::GFP_Screen_Tidy"
author: "Nathan Brandt"
date: "7/6/2018"
output: html_document
---

#1) Two samples in four media types analyzed on the Accuri in triplicate .
#    Strains-
#     GAP1::GFP KO Collection Pool
#     Strains have GFP fused with GAP1 and tdTomato expressed under the ACT1 promoter in the HO locus
#    Media Types-
#     SC
#     Proline Limited Media
#   Controls-
#      FY4 in Proline Limited Media
#      FY4 in SC Media
#      GFP::GAP1 HISKO in Proline Limited Media
#      GFP::GAP1 HISKO in SC Media

###This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters
* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed

******

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Step 1: Load relevant libraries 

```{r}
# This is a function that just makes sure you have a package, or installs it for you without prompting

requireInstall <- function(packageName,isBioconductor=F) {
  if ( !try(require(packageName,character.only=T)) ) {
    print(paste0("You don't have ",packageName," accessible, ",
      "I'm gonna install it"))
    if (isBioconductor) {
      source("http://bioconductor.org/biocLite.R")                        
      biocLite(packageName)                                                 
    } else {
      install.packages("packageName", repos = "http://cran.us.r-project.org")
    }
  }
  return(1)
}

#Load libraries
requireInstall("tidyverse")
```

## Including Plots


```{r pressure, echo=FALSE}
plot(pressure)
```


