---
title: "Flow_Cytometry_GAP1:GFP Screen Analysis"
author: "Nathan Brandt"
date: "Sept 19th, 2016"
output: html_document
---
#1) Two samples in four media types analyzed on the Accuri in triplicate .
#    Strains-
#     GAP1::GFP KO Collection Pool
#     Strains have GFP fused with GAP1 and tdTomato expressed under the ACT1 promoter in the HO locus
#    Media Types-
#     SC
#     Proline Limited Media
#   Controls-
#      FY4 in Proline Limited Media
#      FY4 in SC Media
#      GFP::GAP1 HISKO in Proline Limited Media
#      GFP::GAP1 HISKO in SC Media

###This code is designed for use with the Accuri flow cytometer, which is equiped with the following lasers and filters
* Blue laser (488 nm)
  + FL1 filter = 514/20nm   GFP
  + FL3 filter = 575/25nm   YFP

* Yellow/green laser (552 nm)
  + FL2 filter = 610/20nm   mCherry, dtomato
  + FL4 filter = 586/15nm   DsRed

******
##Step 1: Load relevant libraries 

```{r}
#Load libraries
library(flowCore)
library(flowViz)
#library(flowQ) #Not Availible in R 3.3.1
#library(flowStats) #Not Availible in R 3.3.2
#library(Hmisc) #Not Availible in R 3.3.2
library(reshape2)
library(ggplot2)
#library(flowWorkspace) #Not Availible in R 3.3.2
#library(ggcyto) #Not Availible in R 3.3.2
library(gridExtra)
```

###Step 2: Read in all .fcs files in current directory and a sample sheet that contains four columns with 
* column1 = Well
* column2 = Strain
* column3 = Genotype
* column4 = Ploidy
* column5 = Media


```{r}
#Set working directory to the folder in which you have stored your .fcs files
#Read in all the fcs files in the directory, with alter.ames changing "-" to "."

#Variables for scanning through mulitple plates

<<<<<<< HEAD
plate <- "14TestRun" #Plate number, under 10 need 0#
condition <- "ProLim" #Media type and/or other conditions, SC or ProLim
path.data <-"~/Google Drive/Transfer_Folder/GAP1_GFP_Screen/" #location of data files
path.save <-"~/Google Drive/Transfer_Folder/GAP1_GFP_Screen/Reports"#location to save files
=======
<<<<<<< HEAD
plate <- "14TestRun" #Plate number, under 10 need 0#
condition <- "ProLim" #Media type and/or other conditions, SC or ProLim
path.data <-"~/Google Drive/Transfer_Folder/GAP1_GFP_Screen/" #location of data files
path.save <-"~/Google Drive/Transfer_Folder/GAP1_GFP_Screen/Reports"#location to save files
=======
plate <- "19" #Plate number, under 10 need 0#
condition <- "ProLim" #Media type and/or other conditions, SC or ProLim
path.data <-"~/Google Drive/Transfer_Folder/GAP1_GFP_Screen/" #location of data files
path.save <-"~/Flow_Cytometry_Analysis/GAP1-GFP_Screen/Reports"#location to save files
>>>>>>> 00b624f77b837fd206ffc1eec132cde541d161d8
>>>>>>> fa6727bb6816c207cbbbe379a71a281fd1afecee

  threshold.z_scores <- 2 # cutoff for z-scores to isolate
  threshold.count <- 10000 # cutoff for number of events to isolate

samplesize <- NULL #Number of Random Lines from the FSC files to read in, set to NULL to read all lines

flowData <- read.flowSet(path = paste(path.data,"GAP1_GFP_Screen_FSC_Files/Plate",plate,"_",condition, sep=""), pattern=".fcs", which.lines=samplesize, alter.names=TRUE)

sample.sheet <- read.csv(paste(path.data,"GAP1_GFP_Screen_DataSheets/Plate",plate,"_",condition,".csv", sep=""))
```

```{r}
#Read in and parse OD files
#Plate01 and Plate02 have no OD readings
#Plate03 only has Ctrl OD readings for duplicates of FY4 and HIS3KO in rows A,B,F, and G
#Ctrls are in triplicates
#FY4 in Proline is in Column 04 Rows ABC
#FY4 in SC is in Column 08 Rows ABC
#DGY1215-HIS3KO in Proline is in Column 04 Rows FGH
#DGY1215-HIS3KO in SC is in Column 08 Rows FGH

od.ctrl.blank <-read.table(file=paste(path.data,"GAP1_GFP_Screen_ODs/Plate",plate,"_Ctrls_Blank.asc",sep=""), row.names=1, header=T)
od.ctrl <-read.table(file=paste(path.data,"GAP1_GFP_Screen_ODs/Plate",plate,"_Ctrls.asc",sep=""), row.names=1, header=T)
od.plate.blank <-read.table(file=paste(path.data,"GAP1_GFP_Screen_ODs/Plate",plate,"_",condition,"_Blank.asc",sep=""), row.names=1, header=T)
od.plate <-read.table(file=paste(path.data,"GAP1_GFP_Screen_ODs/Plate",plate,"_",condition,".asc",sep=""), row.names=1, header=T)

od.plate.adjust <- od.plate-od.plate.blank
ctrl.od.adjust <- od.ctrl-od.ctrl.blank

od.data <- data.frame(WELL=sample.sheet$Well, STRAIN=sample.sheet$Strain, OD=NA)

#This code will input the correct ODs into the data.frame
for(i in 1:96){
  od.data$OD[i] <- as.list(t(od.plate.adjust))[i]
}

for(i in 1:((nrow(od.data)-96)/4)){
   od.data$OD[93+(4*i)] <- ctrl.od.adjust[i,4]
    od.data$OD[94+(4*i)] <- ctrl.od.adjust[i,8]
    od.data$OD[95+(4*i)] <- ctrl.od.adjust[i+5,4]
    od.data$OD[96+(4*i)] <- ctrl.od.adjust[i+5,8]
}

#cleans up the od data.frame
od.data$OD <- as.numeric(od.data$OD)
```

#Gating of data, and filtering
```{r}

##Apply a rectangle gate based on FSC and SSC to remove values that we have determined are typically debris for haploid cells.  This should be adjusted if the cell type is different
rectGate <- rectangleGate("FSC.A"= c(5.6,7.6),"SSC.A" = c(4.6,6.8))

#Subset the filtered data to remove outliers defined by FFC and SSC 
filterData <- flowData#Subset(flowData, rectGate) 
```

#Plot the rectangle gate used for filtering and determine the proportion of cells used for subsequent analysis
```{r eval=FALSE}
#Not currently using
##Plot Foward vs. Scatter using ggcyto Use to help gate
ggcyto(flowData, aes(x = FSC.A, y = SSC.A), )+
  geom_hex(bins=512)+
  theme(legend.position="none")+
  labs_cyto(labels="channel")
 # scale_x_logicle(w=.5,t=10000,m=4.5)+
  #scale_y_logicle(w=.5,t=10000,m=4.5)
```

###Plot an overview of the data
```{r eval=FALSE}
#Not currently using
##Plot FL1(GFP) versus FSC 
ggcyto(flowData[1], aes(x = FL1.A, y = FSC.A))+
  geom_hex(bins=256)+
  scale_x_log10()+
  scale_y_log10()

##Plot FFS versus SSC
ggcyto(flowData[1], aes(x = SSC.A, y = FSC.A))+
  geom_hex(bins=256)+
  scale_x_log10()+
  scale_y_log10()

```


#Transfer data into a dataframe and produce summary stats
```{r}
#Summary Statistics of Normalized Filtered Data
#Move filtered data into a dataframe
filter.data <- data.frame(FSC.A=NA,SSC.A=NA,FL1.A=NA,WELL=NA,STRAIN=NA)
stats.data <- data.frame(WELL=NA,STRAIN=NA,COUNT=NA,MEDIAN=NA,MEAN=NA,SD=NA,VAR=NA)

for(i in 1:length(filterData)){
  fsc.a <- exprs(filterData[[i,1]])
  ssc.a <- exprs(filterData[[i,2]])
  fl1.a <- exprs(filterData[[i,3]])
  well <- unlist(strsplit(rownames(pData(filterData)),'.fcs'))[i]
  strain <- as.character(sample.sheet[i,3])
  
  filter.data<-rbind(filter.data,cbind(FSC.A=fsc.a,SSC.A=ssc.a,FL1.A=fl1.a,WELL=well,STRAIN=strain))
  
  stats.data<-(rbind(stats.data,cbind(WELL=well,STRAIN=strain,COUNT=length(fsc.a),MEDIAN=median(fl1.a/fsc.a),MEAN=mean(fl1.a/fsc.a),SD=sd(fl1.a/fsc.a),VAR=as.numeric(var(fl1.a/fsc.a)))))
}  
  
 #Cleans up DataFrames
  filter.data<-filter.data[2:nrow(filter.data),]
  filter.data$FSC.A<-as.numeric(filter.data$FSC.A)
  filter.data$SSC.A<-as.numeric(filter.data$SSC.A)
  filter.data$FL1.A<-as.numeric(filter.data$FL1.A)
  filter.data$WELL<-as.factor(filter.data$WELL)
  filter.data$STRAIN<-as.factor(filter.data$STRAIN)
  
  stats.data<-stats.data[2:nrow(stats.data),]
  stats.data$WELL<-as.factor(stats.data$WELL)
  stats.data$STRAIN<-as.factor(stats.data$STRAIN)
  stats.data$COUNT<-as.numeric(stats.data$COUNT)
  stats.data$MEDIAN<-as.numeric(stats.data$MEDIAN)
  stats.data$MEAN<-as.numeric(stats.data$MEAN)    
  stats.data$SD<-as.numeric(stats.data$SD)
  stats.data$VAR<-as.numeric(stats.data$VAR)
  
```

#Z-Scores
```{r}
#Caluclates the mean and standard deviation of the GFP Signal normalized by forward scatter from the HIS3KO_Proline Control Strains
m.ctrl <- mean(filter.data$FL1.A[filter.data$STRAIN=='HIS3KO_Pro_Lim']/filter.data$FSC.A[filter.data$STRAIN=='HIS3KO_Pro_Lim'])
sd.ctrl <- sd(filter.data$FL1.A[filter.data$STRAIN=='HIS3KO_Pro_Lim']/filter.data$FSC.A[filter.data$STRAIN=='HIS3KO_Pro_Lim'])
  
#Caluclates the mean and standard deviation of the GFP Signal normalized by forward scatter  from the HIS3KO strains
m.HIS3KO <- mean(filter.data$FL1.A[filter.data$STRAIN=='YOR202W_HIS3']/filter.data$FSC.A[filter.data$STRAIN=='YOR202W_HIS3'])
sd.HIS3KO <- sd(filter.data$FL1.A[filter.data$STRAIN=='YOR202W_HIS3']/filter.data$FSC.A[filter.data$STRAIN=='YOR202W_HIS3'])

#Caluclates the mean and standard deviation of the GFP Signal normalized by forward scatter  from the plate
m.pop <- mean(filter.data$FL1.A/filter.data$FSC.A)
sd.pop <- sd(filter.data$FL1.A/filter.data$FSC.A)

#creates an empty variable to store the z.scores
z_scores <- data.frame(Strain=NA, Well=NA, Z_Score_Ctrl=NA, Z_Score_HIS3KO=NA, Z_Score_Pop=NA)

#calucaltes the z-scores based on the well's standard deviation from either all the populations of the plate or the populations of HIS3KO
for(i in 1:nrow(sample.sheet)){
  
  z.ctrl <- (stats.data$MEAN[i]-m.ctrl)/sd.ctrl
  z.HIS3KO <- (stats.data$MEAN[i]-m.HIS3KO)/sd.HIS3KO
  z.pop <- (stats.data$MEAN[i]-m.pop)/sd.pop
  
  z_scores <- rbind(z_scores, cbind(Strain=as.character(sample.sheet$Strain[i]),Well=as.character(sample.sheet$Well[i]),Z_Score_Ctrl=z.ctrl,Z_Score_HIS3KO=z.HIS3KO,Z_Score_Pop=z.pop))
}

#cleans-up the list of z-scores
  z_scores<-z_scores[2:nrow(z_scores),]
  z_scores$Strain<-as.factor(z_scores$Strain)
  z_scores$Well<-as.factor(z_scores$Well)
  z_scores$Z_Score_Ctrl<-as.numeric(z_scores$Z_Score_Ctrl)
  z_scores$Z_Score_HIS3KO<-as.numeric(z_scores$Z_Score_HIS3KO)
  z_scores$Z_Score_Pop<-as.numeric(z_scores$Z_Score_Pop)
```

#Identifying Mutants of Interest
```{r}
  #Create the data frame to store the flagged wells
  flag.data <- data.frame(STRAIN=sample.sheet$Strain, WELL=sample.sheet$Well,Z_Score_Ctrl=FALSE,Z_Score_HIS3KO=FALSE,Z_Score_Pop=FALSE,Count=FALSE)
  
  #Goes through each well and sets each flagged value to TRUE
  for(i in 1:nrow(flag.data)){
    if(abs(z_scores$Z_Score_Ctrl[i])>=threshold.z_scores){flag.data$Z_Score_Ctrl[i] <- TRUE}
    if(abs(z_scores$Z_Score_HIS3KO[i])>=threshold.z_scores){flag.data$Z_Score_HIS3KO[i] <- TRUE}
    if(abs(z_scores$Z_Score_Pop[i])>=threshold.z_scores){flag.data$Z_Score_Pop[i] <- TRUE}
    if(abs(stats.data$COUNT[i])<threshold.count){flag.data$Count[i] <- TRUE}
  }
```

#Add Flags to Filtered Data dataframe
```{r}
    #Combines the flagged well data, and the actual data in one data frame. This seems to be nessasry to easily plot the data
    filter.data <- cbind(filter.data, Z_Score_HIS3KO=FALSE, Count=FALSE)
    od.data <- cbind(od.data, Z_Score_HIS3KO=FALSE, Count=FALSE)
    
  
  for(i in 1:nrow(filter.data)){
    if(abs(z_scores$Z_Score_HIS3KO[z_scores$Well==filter.data$WELL[i]])>=threshold.z_scores){filter.data$Z_Score_HIS3KO[i] <- TRUE}
    if(abs(stats.data$COUNT[z_scores$Well==filter.data$WELL[i]])<threshold.count){filter.data$Count[i] <- TRUE}
  }
  for(i in 1:nrow(od.data)){
    if(abs(z_scores$Z_Score_HIS3KO[z_scores$Well==od.data$WELL[i]])>=threshold.z_scores){od.data$Z_Score_HIS3KO[i] <- TRUE}
    if(abs(stats.data$COUNT[z_scores$Well==od.data$WELL[i]])<threshold.count){od.data$Count[i] <- TRUE}
  }
    
```

#Stats and Flagged Mutants
```{r}
    # Prints out the stats and the flagged data
    print(stats.data)
    
    print(z_scores)
    
    print(flag.data)
```

#Plots of Flagged Data
```{r}
  #Plots the flagged data's Forward vs. Side Scatter Plots, and FL1 vs Forward Plots, plus the OD of the wells. All compared to the HIS3KO wells
  flagged.plots <- list()
  flagged.plots[[1]] <- ggplot(subset(filter.data,((filter.data$STRAIN=='YOR202W_HIS3')|(filter.data$Z_Score_HIS3KO==TRUE))), aes(x = FSC.A, y = SSC.A))+
    geom_hex(bins=512)+
    facet_wrap(~STRAIN,ncol=4)+
    theme(legend.position="none")+
    labs(title= paste("FSC.AvSSC.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_x_log10()+
    scale_y_log10()
  flagged.plots[[2]] <- ggplot(subset(filter.data,((filter.data$STRAIN=='YOR202W_HIS3')|(filter.data$Z_Score_HIS3KO==TRUE))), aes(x = FSC.A, y = FL1.A))+
    geom_hex(bins=512)+
    facet_wrap(~STRAIN,ncol=4)+
    theme(legend.position="none")+
    labs(title= paste("FSC.AvFL1.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_x_log10()+
    scale_y_log10()
#Plot of OD Data
  flagged.plots[[3]] <-ggplot(subset(od.data,((od.data$STRAIN=='YOR202W_HIS3')|(od.data$Z_Score_HIS3KO==TRUE))), aes(WELL,OD))+
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    geom_point() +
    labs(title= paste("ODs_Plate",plate,"_",condition, sep="")) +
    scale_x_discrete(labels=subset(od.data$STRAIN,((od.data$STRAIN=='YOR202W_HIS3')|(od.data$Z_Score_HIS3KO==TRUE))))+
    xlab("STRAIN")
  
  flagged.plots
  
    ggsave(paste(path.save,"Flagged_Strains_Plate",plate,"_",condition,"_Threshold_",threshold.z_scores,".pdf", sep=""), plot=  marrangeGrob(grobs = flagged.plots, nrow=1, ncol=1),
 height=8, width=12)
    
```

#Plots of Data
```{r eval=FALSE}
  # Set to FALSE because I want to only look at the flagged data
  #Plots all the wells forward vs side plots, and the boxplots of the various paramenters, and OD
dir.create(paste(paste(path.save,"Plate",plate,"_PDFs/",sep="")))
#Plots of FSC VS SSC
size.plots <- list()
left <- 1
right <- sum(stats.data$COUNT[1:18])
size.plots[[1]] <- ggplot(filter.data[left:right,], aes(x = FSC.A, y = SSC.A))+
    geom_hex(bins=512)+
    facet_wrap(~ WELL + STRAIN,nrow=3)+
    theme(legend.position="none")+
    labs(title= paste("FSC.AvSSC.A_Filtered_Plate",plate,"_",condition,"_Page",1, sep="")) +
    scale_x_log10()+
    scale_y_log10()

for(i in 2:((ceiling(nrow(stats.data)/18))-1)){
  left <- right+1
  right <- right+sum(stats.data$COUNT[(1+(18*(i-1))):(18+(18*(i-1)))])
  
  size.plots[[i]] <- ggplot(filter.data[left:right,], aes(x = FSC.A, y = SSC.A))+
    geom_hex(bins=512)+
    facet_wrap(~ WELL + STRAIN,nrow=3)+
    theme(legend.position="none")+
    labs(title= paste("FSC.AvSSC.A_Filtered_Plate",plate,"_",condition,"_Page",i, sep="")) +
    scale_x_log10()+
    scale_y_log10()
}

i<-i+1
left <- right+1
size.plots[[ceiling(nrow(stats.data)/18)]] <- ggplot(filter.data[left:nrow(filter.data),], aes(x = FSC.A, y = SSC.A))+
    geom_hex(bins=512)+
    facet_wrap(~ WELL + STRAIN,nrow=3)+
    theme(legend.position="none")+
    labs(title= paste("FSC.AvSSC.A_Filtered_Plate",plate,"_",condition,"_Page",i, sep="")) +
    scale_x_log10()+
    scale_y_log10()

size.plots
ggsave(paste(path.save,"Plate",plate,"_PDFs/FSC.AvsSSC.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), plot=size.plots height=8, width=12)
    
    
#Plots of FSC Data
ggplot(filter.data, aes(WELL,FSC.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= paste("FSC.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/FSC.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)

#Plots of SSC Data
ggplot(filter.data, aes(WELL,SSC.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= paste("SSC.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/SSC.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)

#Plot of FL1 Data
ggplot(filter.data, aes(WELL,FL1.A)) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= paste("FL1.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/F1.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)

#Plot of FL1/FSC Data
ggplot(filter.data, aes(WELL,(FL1.A/FSC.A))) +
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    stat_boxplot(geom ='errorbar') +
    geom_boxplot(outlier.shape = NA) +
    labs(title= paste("FL1.A/FSC.A_Filtered_Plate",plate,"_",condition, sep="")) +
    scale_y_log10()+
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/FL1.ANormFSC.A_Filtered_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)

#Plot of OD Data
ggplot(od.data, aes(WELL,OD))+
    theme_bw() +
    theme(axis.text.x = element_text(angle = 90,vjust=0.5,hjust = 1, size = 6)) +
    geom_point() +
    labs(title= paste("ODs_Plate",plate,"_",condition, sep="")) +
    scale_x_discrete(labels=sample.sheet$Strain)+
    xlab("STRAIN")
ggsave(paste(path.save,"Plate",plate,"_PDFs/ODs_Plate",plate,"_",condition,".pdf", sep=""), height=8, width=12)
```